Appendix

### 2020-05-02 appendix/appendixV5.Rmd
Fix Table 2 and Table 3.

```{r, echo=F}

# Table - General

aux <- dat %>%
  group_by(depvar2) %>%
  summarise(n = n(),
            mean_coef = mean(coef, na.rm = T),
            median_coef = median(coef, na.rm = T)) %>%
  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
  select(depvar2, n, pct, mean_coef, median_coef) %>%
  rename(` ` = depvar2,
         N = n,
         Pct = pct,
         Mean = mean_coef,
         Median = median_coef)

@@

### Descriptive Stats of Moderators by Year

```{r, echo=F}

#Table: by year

aux <- dat %>%
  group_by(depvar2, year) %>%
  summarise(n = n(),
            mean_coef = round(mean(coef, na.rm = T), digits = 3),
            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
  group_by(year) %>%
  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
  arrange(year) %>%
  rename(` ` = depvar2,
         Year = year,
         N = n,
         Pct = pct,
         Mean = mean_coef,
         Median = median_coef
         )

@@

mod1 <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod1_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod2 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod2_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod3 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod3_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod4 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod4_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod5 <- tibble(
   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod5_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod6 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod6_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(type = "Base") %>%
  select(type, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(type = "All Coefs") %>%
  select(type, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"))

@@

\blandscape
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = T,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value"
      )
    ) %>% 
  collapse_rows(
    1:3,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

>>>>

```{r, echo=F,warning=F,message=F,error=F}

# Table 2

dat2 <- dat %>%
  select(depvar2, indepvar2, published, elecsys2, method,agglevel, location2) %>%
  rename(Depvar = depvar2,
         Indepvar = indepvar2,
         Published = published,
         "Electoral System" = elecsys2,
         Method = method,
         "Aggregate Level" = agglevel,
         Location = location2)

names <- dat2 %>% 
  map(table) %>%
  unlist() %>%
  names()

aux <- dat2 %>%
  map_df(~{
    table(.x) %>%
      as.data.frame() %>%
      rename(Moderator = ".x") %>%
      mutate(Moderator = as.character(Moderator),
             Pct = paste0(100*(round(Freq/sum(Freq, na.rm = T), digits = 4)), "%"))
  }) %>%
  mutate(Moderator = names,
         Moderator = gsub("\\.", ": ", Moderator),
         Freq = as.character(Freq)) %>%
  bind_rows(.,
            tibble(
              Moderator = "Year",
              Freq = paste0(round(mean(dat$year, na.rm = T), digits=2), " (Mean)"),
              Pct = paste0(as.character(round(median(dat$year, na.rm = T), digits=2)), " (Median)")
            ))

@@

rm(dat2,names)
```

@@

mod1 <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

@@

mod1_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod2 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod2_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod3 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod3_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod4 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod4_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod5 <- tibble(
   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod5_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod6 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

mod6_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)

@@

\blandscape

## Summary of Results
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

```{r, echo=F, warning=F,error=F,message=F}
coefs = bind_rows(
  mod1_permu,
  mod2_permu,
  mod3_permu,
  mod4_permu,
  mod5_permu) %>%
  select(` `) %>%
  distinct()

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)

\blandscape

## Summary of Results (Permutation)
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      "latex",
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))
